Import_JazEmData

### 2024-01-15 Code/Import_JazEmData.Rmd
Tidied scripts
Corrected incorrect variable name for unnest column

JazSpecNest <- MC_SpectraPAR %>%
  nest(Spectra = c(MCEm_nm, Emission))

@@

JazSpecNest %>%
  unnest(Spectra) %>%
    ggplot() +
  geom_point(aes(x = MCEm_nm, y = Emission, colour = as.factor(WL))) +
  geom_text(aes(x = EmMax_nm, y= max(Emission), label= EmMax_nm), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
  scale_color_manual(values = MCMIXColours) +
  guides(colour = "none") +
  geom_vline(aes(xintercept = EmMax_nm), linetype = "dashed") +
  scale_y_continuous(limits = c(0,100000)) +
  ggh4x::facet_nested(rows = vars(MC, WL), labeller = labeller(WL = label_both, Par = label_both, MultiCulti = label_both)) +
  theme_bw()

>>>>

JazSpecNest <- MC_SpectraPAR %>%
  nest(EmSpectra = c(MCEm_nm, Emission))

@@

JazSpecNest %>%
  unnest(EmSpectra) %>%
    ggplot() +
  geom_point(aes(x = MCEm_nm, y = Emission, colour = as.factor(WL))) +
  geom_text(aes(x = EmMax_nm, y= max(Emission), label= EmMax_nm), alpha = 0.5 ,hjust = 0.5, vjust=-0.5) +
  scale_color_manual(values = MCMIXColours) +
  guides(colour = "none") +
  geom_vline(aes(xintercept = EmMax_nm), linetype = "dashed") +
  scale_y_continuous(limits = c(0,100000)) +
  ggh4x::facet_nested(rows = vars(MC, WL), labeller = labeller(WL = label_both, Par = label_both, MultiCulti = label_both)) +
  theme_bw()
